\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-09-17 manuscript.Rmd
Adding text to Methods section

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
  latex_engine: xelatex
mainfont: Helvetica

---

@@

# Introduction
Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
# Methods

@@

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desctable.data %>%
  tbl_summary(
    by = IncludedInCFA,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>%
as_kable(format = 'pipe') -> desc_kable #save it as a kable

@@

desc_kable

@@

Table 1 summarizes the demographic characteristics of the online survey participants. Anonymous online questionnaire responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. The EFA sample included participants filling out the questionnaire from XX.XX.XXXX to YY.YY.YYYY, whereas participants who filled out the questionnaire from ZZ.ZZ.ZZZZ to 03.09.2021 were included in the CFA analysis. Participants reported filling out the online survey from a diverse range of geographic locations. The four most common geographic locations included:

@@

We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2). @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Among the 23 items, 10 items were highly discriminating. Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
mainfont: Arial
---

@@

# Introduction

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017] \# Methods

## Ethical approval

The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl. Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data. An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."

## Data Availability

## Survey characteristics

Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [CITE REDCAP HERE 1, 2] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>). Participants for the anonymous online survey were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].

Completing the online survey took approx. 15 to 20 minutes and was not compensated. The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed. Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey. Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey. Moreover, participants needed to confirm that they were participating the survey for the first time. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). The data analysed in this study was collected between 17.05.2021 and 03.09.2021. Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.

In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:

-   Sleep disturbance and sleep-related impairment [CITE]
-   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
-   Meal timing & caffeine consumption [CITE]
-   Light sensitivity (photophobia vs. photophilia) [CITE]
-   Self-reported pubertal stage (only if younger than 18 years old) [CITE]

Furthermore, the following 1-item demographic variables were assessed:

-   Age
-   Sex
-   Gender identity
-   Occupational Status
-   COVID-related Occupational setting during the past four weeks
-   Time zone & country of residence
-   English as native language

@@

# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
desctable.data %>%
  tbl_summary(
    by = IncludedInCFA,
    statistic = list(all_continuous() ~ "{mean} ({sd})",
                     all_categorical() ~ "{n} ({p}%)"),
    digits = all_continuous() ~ 2,
    label = list(slypos_demographics_age ~ "Age",
                 slypos_demographics_sex.factor ~ "Sex",
                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
                 slypos_demographics_language.factor ~ "Native English Speaker",
                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
                 slypos_demographics_school.factor ~ "Occupational setting"
                 ),
    missing = "no"
    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
modify_header(label ~ "**Variable**") %>% 
as_kable(format = 'pipe') -> desc_kable #save it as a knitr::kable

@@

desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")

@@

Table 1 summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. XX participants were excluded from analysis due to not passing at least one of the "attention check" items. Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1. EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2. CFA Sample",])`). The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis. Participants indicated filling out the online survey from a diverse range of geographic locations. The four most common geographic locations included:

`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`

For a full list of geographic locations, see Suppl. Table X in the appendix.

Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years (EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`), with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age (Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1. EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2. CFA Sample"])`). In total 47% of participants indicated female sex (EFA: 44%; CFA: 52%), 51% indicated male (EFA: 54%; CFA: 46%) and 2% indicated other sex (EFA: 2.1%, CFA: 1.9%). Overall 7.2% (EFA: 7.8%; CFA: 6.2%) participants indicated a gender-variant identity. In a "Yes/No" question regarding native language 46% of respondents (EFA: 46%; CFA: 45%) indicated to be native English speakers. For their "Occupational Status", more than half (57%) of the overall sample reported that they currently work (EFA: 55%; CFA: 61%), whereas 25% (EFA: 29%; CFA: 20%) reported that they go to school and 17% (EFA: 17%; CFA: 19%) responded that they do neither. With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 44% (EFA: 45%; CFA: 42%) of the participants indicated that they were in a home office/ home schooling setting., while 16% overall (EFA: 16%; CFA: 16%) reported face-to-face work/schooling. Lastly, 21% overall (EFA: 22%; CFA: 20%) reported a combination of home- and face-to-face work/schooling, whereas 19% overall (EFA: 17%; CFA: 23%) filled in the "Neither (no work or school, or indication)" response option. We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [CITE]. The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package. After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ .2, indicating equivalence.

@@

We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality. In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2). @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70. Among the 23 items, 10 items were highly discriminating. Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute. Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
